\chapter{Ethical Analysis}

Before developing our product, there are several ethical scenarios that need to be considered and addressed.
First, we must acknowledge internal ethical dilemmas that we may encounter.  The first of which is ensuring that every team member has a voice that is heard during the design process.  No member of our team should be ignored or blocked from the development process under any circumstances.  On the opposite end, no member should be forced to perform a greater amount of work than the rest of the group.  The workload should be distributed among team members as evenly as possible.  To prevent either of these ethical issues during the design, one solution is to document every necessary next steps as well as all recently completed steps when all members are present, or on an online forum that all members have access to.  This will allow all members to be aware of and able to add input to every task, preventing anyone from being blocked from development information.  And this will allow all members to see who has done which tasks, so it will be easy to determine if the work load is being divided fairly.

Secondly we must acknowledge external ethical dilemmas that could be pertinent to our product.  One of which, is ensuring that our product works for people of all races and genders.  We do not want a product that is implicitly racist or sexist due to its code.  In order to ensure this is not the case, we plan on having  diverse data that incorporates people of all races and genders, as well as test cases that confirm all people will be able to share the same experience while using our product.