\chapter{Introduction}
Taking pictures to save our best memories is a common practice. During group pictures, photos can be entirely ruined by a single person?s expressions. We all have seen photos of people who did not smile/looked away, or worse, been that person. The experiences at big events and gatherings would be much more fulfilling if we didn?t have to take many pictures just to get a nice smiling photo. Modern cameras and phones have beautiful design incorporated with advanced features. However, they have forgotten to address this pesky issue that would uplift everyone?s picture taking moment. 

Currently, the only group photo technology to be created is the automatic photo with timer.  The purpose of this is to eliminate the need for someone to click the button to take the photo, however it is not smart.  It does not signal when the photo will be taken, and takes the photo only when the timer has reached zero.  Therefore, this does not have any effect on the quality of the photo.  Currently, the only solutions affecting the quality of group photos are after effect softwares such as photoshop.  However, these often require a large amount of money, and a level of skill in using the product, which most people don?t have.

We propose to build an iOS app that utilizes the iPhone?s camera and adds the feature of taking pictures automatically when everyone in the group is looking at the camera with their eyes open and smiling. The app will automate the tedious task of capturing the right moment saving people?s time for actually enjoying the moment.  Computer vision will be used to narrow the focus of the image, to then allow a machine learning model to determine when the right moment to snap the photo is.

To conclude, our design will accomplish two things: firstly, it will save time for both people who are getting their photo taken as well as the person taking the photo, as the camera will know exactly when to take the right photo, and secondly, will improve the quality of photos, allowing for memories to be better cherished by all. 


